Analytic Doppler Imaging

### 2019-07-30 tex/gitlinks.tex
beefing up the Doppler class

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/2720441d1bd09da0ba8e768041eb50d5230512fc/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}

>>>>

\newcommand{\codelink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/figures/#1.py}{\codeicon}\,\,}
\newcommand{\animlink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/figures/#1.gif}{\animicon}\,\,}
\newcommand{\prooflink}[1]{\href{https://github.com/user/repo/blob/06d5b85a111d278d05c6eec5df6638f529432379/tex/proofs/#1.ipynb}{\raisebox{-0.1em}{\prooficon}}}
